Updates on the Exoplanet Orbit Database

### 2014-02-25 draft/ms.tex

%------------------------------------------------------------------------------
\subsection{Planet Information}

We report basic planet information to give our users general
information of when, by whom and how the planets were
discovered. Since \cite{Wright2011}, as more planets were discovered
by different methods other than radial velocity and transit, we have
expanded this information to better ingest those planets into our
database.

KEPID stands for KEPler ID which is the integer number assigned for Kepler host stars. KEPID is only available for the unconfirmed KOIs which we import directly from the Exoplanet Archive. Therefore, none of the EOD planets and the Kepler planets do not have KEPID.

KOI stands for `Kepler Objects of Interest' which is a star suspected to host transiting exoplanet. Transit signals are detected by \kepler\ but have not been confirmed to be planets. KOI field contains floating points that is consisted of a whole number designated to the host star followed by a decimal number denoting candidate planets. For example, KOI 102 is a star suspected to host multiple exoplanets and KOI 102.01 is an inner and KOI 102.02 is an outer planet candidate. Once the candidates are confirmed to be planets, the host star is designated \kepler\ followed by a hyphen and an integer. 
\textit {I am not actually sure why we started reporting KOI numbers... maybe to better track of exoplanets?}

\textit {Sharon: you need to say what KOI stores. When writing each
  field, keep in mind you need to cover the following so that the
  reader will completely understand: (1) what the field stands for
  (e.g., in case of an abbreviation like KOI); (2) what the field
  physically means, like `KOI' means planet candidates that have transit
  signals as detected by \kepler\ but have not been confirmed, and
  make sure to be thorough at what you say -- sometimes things are not
  that obvious to an outsider reader, e.g., think if a cosmologist
  would understand what you're saying when reading it; (3) what the
  field actually contains, e.g. KOI contains the KOI number designated
  by the \kepler\ team (right?), it is a floating point number, and
  sometimes maybe even worth giving an example, e.g. KOI 30.1 or
  something...; (4) why we added this new field, if this information
  is helpful, or if it's a revised field since \cite{Wright2011}, what
  is changed. Also, use \kepler\ (which is a defined symbol in our ms.tex file),
  instead of typing out Kepler, since you need italic.
  Don't be afraid to write more! Being concise is important, but it's
  always easier to trim down things than to add things on, especially
  for a documentation type of paper like this. Let's be thorough at
  first, then try to reach optimal conciseness.}

@@

EOD: A planet with the EOD flag being true indicates that it has
well-characterized orbital parameters such as PER, ECC, K, OM, and I
and is thus included in the EOD. We added this field because
exoplanets.org now also includes robustly discovered planets that do
not have well-characterized orbits, and also \kepler\ planet
candidates (see Section~\ref{sec:kepler} for more details).

MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENSING, IMAGING, TIMING and ASTROMETRY flags which are boolean numbers. Any of these flag being true indicates that the planet is detected by the method. For example, MICROLENSING flag being 1 means the planet is detected by microlensing event. Planets primarily detected
by these methods do not have robust orbital parameters, they are
categorized as ``Other Planets'' on exoplanets.org. However, we require the detection to be robust, as determined by the QUAlity Control Board of the Exoplanet Database, QUACBED. 
If planets have follow up radial velocity or transit observations and
thus have good orbital parameters, they have EOD flags. See
Section~\ref{sec:kepler} for more information about `Other Planets'.

\textit {Sharon: you've changed `discovered' to `detected', but it's
  still not an accurate description. Let's meet and discuss this in
  person. 
  old: Sharon's comments: Instead of saying `discovered', we should say `detected'
  -- some planets are detected by these methods but are not
  necessarily discovered by them at the first place. Re-phrase the
  last sentence -- not all of planets with any of these TRUE are in
  `Other Planets', only some are, so maybe just note planets
  discovered by these methods are not necessarily in EOD and direct
  the reader to Section~\ref{sec:kepler} where we talk about `Other
  Planets'. Remember Section~\ref{sec:update} is focuses on EOD
  updates though the fields apply to all planets on
  exoplanets.org. Need to note here that we require the detection to
  be robust, as determined by the QUAlity Control Board of the
  Exoplanet Database, QUACBED.}

@@

>>>>

%------------------------------------------------------------------------------
\subsection{Discovery and References}

We report general information of when, by whom and how the planets were
discovered and provide the references. We describe the added fields since \cite{Wright2011} below. \\

{\bf KEPID} stands for KEPler ID which is the integer number assigned for a Kepler host star. KEPID is only available for the unconfirmed KOI which we import directly from the Exoplanet Archive. Therefore, none of the EOD planets and the confirmed Kepler planets has KEPID.

{\bf KOI} stands for Kepler Objects of Interest which is a star with transit signals detected by \kepler\ but have not been confirmed to due to exoplanets. The KOI field contains a floating point number that consist of a whole number designated to the host star followed by a decimal number denoting a candidate planet. For example, KOI 102 is a star suspected to host two exoplanets and KOI 102.01 is the inner planet candidate and KOI 102.02 is the outer one. Once a candidate is confirmed, the NAME field of the planet is replaced by the official \kepler\ ID ('Kepler' followed by a hyphen, an integer and a letter). The KOI number is used as OTHERNAME. None of the KOIs are in the EOD and for more information see Section~\ref{sec:kepler}.

\begin{comment}
\textit {Sharon: you need to say what KOI stores. When writing each
  field, keep in mind you need to cover the following so that the
  reader will completely understand: (1) what the field stands for
  (e.g., in case of an abbreviation like KOI); (2) what the field
  physically means, like `KOI' means planet candidates that have transit
  signals as detected by \kepler\ but have not been confirmed, and
  make sure to be thorough at what you say -- sometimes things are not
  that obvious to an outsider reader, e.g., think if a cosmologist
  would understand what you're saying when reading it; (3) what the
  field actually contains, e.g. KOI contains the KOI number designated
  by the \kepler\ team (right?), it is a floating point number, and
  sometimes maybe even worth giving an example, e.g. KOI 30.1 or
  something...; (4) why we added this new field, if this information
  is helpful, or if it's a revised field since \cite{Wright2011}, what
  is changed. Also, use \kepler\ (which is a defined symbol in our ms.tex file),
  instead of typing out Kepler, since you need italic.
  Don't be afraid to write more! Being concise is important, but it's
  always easier to trim down things than to add things on, especially
  for a documentation type of paper like this. Let's be thorough at
  first, then try to reach optimal conciseness.}
 \end{comment}

@@

{\bf EOD} is a flag which indicates whether an exoplanet has well-characterized orbital parameters (e.g. period (PER)). EOD equals 1 means the exoplanet is in the EOD. We added this field because exoplanets.org now also includes robustly discovered planets that do not have well-characterized orbits, and also \kepler\ planet candidates (see Section~\ref{sec:kepler} for more details).

{\bf MICROLENSING, IMAGING, TIMING and ASTROMETRY} are flags which indicate that a planet detected via theses methods. For example, MICROLENSING $=$ 1 means the planet is detected by a microlensing event. However, we require the detection to be robust, as determined by the QUAlity Control Board of the Exoplanet Database, QUACBED.

@@

Since \cite{Wright2011}, as more planets were discovered
by different methods other than radial velocity and transit, we have expanded this information to better ingest those planets into our database.

Planets primarily detected by these methods do not have robust orbital parameters, they are categorized as ``Other Planets'' on exoplanets.org.

If planets have follow up radial velocity or transit observations and
thus have good orbital parameters, they have EOD flags. See
Section~\ref{sec:kepler} for more information about `Other Planets'.
